---
title: "DEOHS Coders Group: Stargazer Practice"
output:
  md_document: default
  word_document: default
  pdf_document:
    toc: true
    toc_depth: 3
  html_document:
    toc: true
    df_print: paged
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T)
```

# Stargazer Overview

Here's a link to the stargazer [package description](https://cran.r-project.org/web/packages/stargazer/stargazer.pdf) and [vingette on CRAN](https://cran.r-project.org/web/packages/stargazer/vignettes/stargazer.pdf). [This recent reddit thread](https://www.reddit.com/r/rstats/comments/8qn43z/what_is_the_best_package_for_displaying_tables_in/) discusses the 'best' packages for displaying tables in R, including kabeExtra, pander, DT, Huxtable, and stargazer. Some users report that stargazer is fast and works easily with a set of regression model objects to produce near-publication quality tables, and can make it pretty simple to compare multiple models side-by-side. Other users, however, have reported challenges related to [hard coding, API, and \LaTeX layout](https://www.reddit.com/r/rstats/comments/6o9v9h/whats_your_favorite_relatively_obscure_r_package/dkgw9q1/). Here's a [stargazer cheat sheet](https://github.com/JakeRuss/cheatsheets/blob/master/stargazer.md) for formatting options.

```{r install-library}
library(pacman)
p_load(stargazer)
```


# Exercise with iris dataset

## Step 1: Display table summary of iris dataset


```{r iris}
summary(iris)
```

### PDF

**1. Stargazer with default settings**

```{r iris-table-summary-pdf-1}
stargazer(iris)
```

**2. Hard-coded (copy and paste from above chunk) works for pdf (but not html)**

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Sepal.Length & 150 & 5.843 & 0.828 & 4.300 & 5.100 & 6.400 & 7.900 \\ 
Sepal.Width & 150 & 3.057 & 0.436 & 2.000 & 2.800 & 3.300 & 4.400 \\ 
Petal.Length & 150 & 3.758 & 1.765 & 1.000 & 1.600 & 5.100 & 6.900 \\ 
Petal.Width & 150 & 1.199 & 0.762 & 0.100 & 0.300 & 1.800 & 2.500 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table} 

**3. Adding results='asis'**

```{r iris-table-summary-pdf-2, results='asis'}
stargazer(iris)
```

### HTML

**4. Changing to type = html**

```{r iris-table-summary-html-1l}
stargazer(iris, type = "html")
```

**5. Hard-coded (copy and paste from above chunk) works for html (but not pdf)**

<table style="text-align:center"><tr><td colspan="8" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">Statistic</td><td>N</td><td>Mean</td><td>St. Dev.</td><td>Min</td><td>Pctl(25)</td><td>Pctl(75)</td><td>Max</td></tr>
<tr><td colspan="8" style="border-bottom: 1px solid black"></td></tr><tr><td style="text-align:left">Sepal.Length</td><td>150</td><td>5.843</td><td>0.828</td><td>4.300</td><td>5.100</td><td>6.400</td><td>7.900</td></tr>
<tr><td style="text-align:left">Sepal.Width</td><td>150</td><td>3.057</td><td>0.436</td><td>2.000</td><td>2.800</td><td>3.300</td><td>4.400</td></tr>
<tr><td style="text-align:left">Petal.Length</td><td>150</td><td>3.758</td><td>1.765</td><td>1.000</td><td>1.600</td><td>5.100</td><td>6.900</td></tr>
<tr><td style="text-align:left">Petal.Width</td><td>150</td><td>1.199</td><td>0.762</td><td>0.100</td><td>0.300</td><td>1.800</td><td>2.500</td></tr>
<tr><td colspan="8" style="border-bottom: 1px solid black"></td></tr></table>

**6. Adding results='asis'**

```{r iris-table-summary-html-2, results='asis'}
stargazer(iris, type = "html")
```

### DOC

**7. Creating single table in word**


```{r iris-table-summary-html-2-doc, results='asis'}
stargazer(iris, type = "html", out="iris-table-summary.doc")
```
> "To include stargazer tables in Microsoft Word documents (e.g., .doc or .docx), please follow the following procedure: Use the out argument to save output into an .htm or .html file. Open the resulting file in your web browser. Copy and paste the table from the web browser to your Microsoft Word document." -[Using stargazer in Word](https://cran.r-project.org/web/packages/stargazer/stargazer.pdf)

## Step 2: Display table models of iris dataset

**8. Creating single model in html**

```{r iris-1-model, results='asis', eval=T}

mtcars$fast <- as.numeric((mtcars$mpg > 20.1)) #Creating a dummy variable 1 = fast car
m1 <- lm(Sepal.Length ~ Sepal.Width, data=iris)

stargazer(m1, type="html")

```

**9. Comparing three models in html**

```{r iris-3-models, results='asis', eval=T}

mtcars$fast <- as.numeric((mtcars$mpg > 20.1)) #Creating a dummy variable 1 = fast car
m1 <- lm(Sepal.Length ~ Sepal.Width, data=iris)
m2 <- lm(Petal.Length ~ Petal.Width, data=iris)
m3 <- lm(Sepal.Length ~ Sepal.Width + Petal.Width + factor(Species), data=iris)

stargazer(m1, m2, m3, type="html")

```


# Exercise with mtcars dataset

<!--Source: https://www.princeton.edu/~otorres/NiceOutputR.pdf-->

```{r mtcars, results='asis', eval=F}


summary(mtcars)


mtcars$fast <- as.numeric((mtcars$mpg > 20.1)) #Creating a dummy variable 1 = fast car
m1 <- lm(mpg ~ hp, data=mtcars)
m2 <- lm(mpg ~ hp + drat, data=mtcars)
m3 <- lm(mpg ~ hp + drat + factor(gear), data=mtcars)
m4 <- glm(fast ~ hp + drat + am, family=binomial(link="logit"), data=mtcars)
stargazer(m1, m2, m3, m4, type="html",
 dep.var.labels=c("Miles/(US) gallon","Fast car (=1)"),
 covariate.labels=c("Gross horsepower","Rear axle ratio","Four foward gears",
 "Five forward gears","Type of transmission (manual=1)"), out="models.htm")
```
